Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-05-18 Manuscript/proto-manuscript.tex
MS: Figures updated

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Fig/HGopsNEWmodels.eps}
  \caption{\label{HGopsNEWmodels}
    Headgroup and glycerol backbone order parameters from standard and EEC models.}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=14.0cm]{../Fig/OrderParameterCHANGESnewMODELS.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of cations from models
    with modified headgroup partial charges.}
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{fig:form-f}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.}
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{HGopsNEWmodels}
    Headgroup and glycerol backbone order parameters from standard Lipid14 and EECLipid17 models.}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2_surf.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of concentration of cations or cationic surfactant DHMDMAB. }
\end{figure}
